mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-12 Draft3.Rmd
errors

It is also possible to use flags for context-dependent rendering. The highlight flag is the default one. It shows where the error is and what is its solution. The ignore flag allows the program to ignore the fact that there is an error and print the expression as if it were correct.  Finally, the third flag, fix, tells you what is the term that you are supposed to fix without giving the solution.  Below the code with its comment is provided.

```{r, results="asis"}
# It highlights what has been omitted
t <- quote(omit_left(a + b))
mathout(t, flags=quote(error(highlight))) # default
```

@@

```{r, results="asis"}
# It prints the incorrect version
mathout(t, flags=quote(error(asis)))
```

```{r, results="asis"}
# It highlights the correct version by framing it
mathout(t, flags=quote(error(fix)))
```

```{r, results="asis"}
# It frames the redundant term
t <- quote(add_right(a + b))
mathout(t, flags=quote(error(highlight))) # default
```

```{r, results="asis"}
# It prints the correct expression without the redundant term
mathout(t, flags=quote(error(ignore)))
```

```{r, results="asis"}
# It strikes the redundant term 
mathout(t, flags=quote(error(fix)))
```

```{r, results="asis"}
# It highlights that a is wrong and b is correct
t <- quote(instead(a, b) + c)
mathout(t, flags=quote(error(highlight))) # default
```

```{r, results="asis"}
# It provides the correct solution
mathout(t, flags=quote(error(ignore)))
```

```{r, results="asis"}
# It provides the correct solution framing the correct term
mathout(t, flags=quote(error(fix)))
```

>>>>

It is also possible to use flags for context-dependent rendering. The `highlight` flag is the default one. It shows where the error is and what is its solution. The `ignore` flag allows the program to ignore the fact that there is an error and print the expression as if it were correct. The third flag, `fix`, tells you what is the term that you are supposed to fix without giving the solution. Finally, the last flag `asis` returns the incorrect expression as the student wrote it, without providing any solutions or corrections.  Below is provided the code with its comment and an example of use.

Let us consider for example a student that instead of writing `b + c` wrote `a+c`.

With the `asis` flag we report the incorrect expression provided by the student:

```{r, results="asis"}
# It prints the incorrect version
t <- quote(instead(a, b) + c)
mathout(t, flags=quote(error(asis)))
```

Then, we may want underline the incorrect term and provide the correct solution.

```{r, results="asis"}
# It underlines what has been incorrect
mathout(t, flags=quote(error(highlight))) # default
```

Alternatively, we can put the correct solution in a box to let the student focus on its correction.

```{r, results="asis"}
# It highlights what has been corrected
mathout(t, flags=quote(error(fix))) 
```

Finally, we can simply provide the correct solution to the problem with the flag `ignore`.

@@
